Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
polished a bit

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions within $R\sim$3.5\,kpc from the galaxy center\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.

In \Fig{MC}, we over-plotted the molecular structures identified using
a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps as an example.
The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
\begin{equation}
{\rm pixel} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
\label{eqn:integrate}
\end{equation} 
where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.

Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
{\AP I fear that putting this subsection here breaks a bit the flow of the analysis of the results. Maybe we can put it as an appendix and keep only eq. 10 in the main text (a put it at when analysing the relevant plot)? }

@@

% PVE
We also compare the MCs identified in our simulations to 
those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of 
\Fig{alpha16}). The V-shaped dashed lines in the figure show the locii along which the given external pressures are needed for 
MCs to have linewidth for a given set of surface densities (see \Sec{PVE}). 
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show the locii along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accreting phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
\label{fig:MR}}
\end{figure*}

@@

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more and less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
in closed box simulations; \citealt{Behrendt16a}). 
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
% 
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas

>>>>

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot 
used to plot \Fig{h2density}.

For visualization, we overplot the molecular structures identified using
a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps 
in \Fig{MC} as an example.
The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
\begin{equation}
{\rm pixel} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
\label{eqn:integrate}
\end{equation} 
where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt 
to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.

Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% \AP{I fear that putting this subsection here breaks a bit the flow of the analysis of the results. Maybe we can put it as an appendix and keep only eq. 10 in the main text (a put it at when analysing the relevant plot)? }

@@

% PVE
We also compare the MCs identified in our simulations to 
those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of 
\Fig{alpha16}). The V-shaped dashed lines in the figure show the loci along which the given external pressures are needed for 
MCs to have linewidth for a given set of surface densities (see \Sec{PVE}). 
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accreting phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
% \citep{Lombardi10a}.
\label{fig:MR}}
\end{figure*}

@@

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently quite expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy 
simulations done at higher resolution (e.g., \citealt{Behrendt16a}). 
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations 
since they adopt non-cosmological initial conditions. 
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
% 
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas
